Optimal Symmetric Multimodal Templates and Concatenated Random Forests for Supervised Brain Tumor Segmentation (Simplified) with ANTsR

### 2014-04-01 paper.tex
WIP: minor abstract edit
ENH: another abstract revison

\begin{abstract} 
Automated brain tumor segmentation in MRI is complicated by the lack of prior knowledge 
concerning tumor location, spatial extent, shape, possible displacement of normal 
tissue, and intensity signature, all of which limit 
the applicability of well-established techniques that have demonstrated good performance 
in related tasks such as normal brain tissue segmentation.  Due to this 
limitation, we localize our prior knowledge strategy through the 
use of subject-specific multimodal asymmetrical features which demonstrate excellent
discriminative properties within the random forest machine learning framework.  
This approach is made possible with symmetric multimodal brain templates which
are optimal in terms of both shape and multivariate intensity.  Further performance improvements are demonstrated by a successive application of random forest models for increasing levels of feature refinement 
 to which we refer as {\it concatenated random forests}.  Although the derived workflow involves many disparate components, the newly developed ANTsR open source software package significantly facilitates the proposed methodology.  ANTsR, a comprehensive interface of the popular Advanced Normalization Tools (ANTs) repository with the R statistical project,
integrates well-performing image analysis tools such as image registration, segmentation, bias correction, and template building with access to advanced statistical and machine learning techniques as well as state-of-the-art visualization possibilities.  
The reported algorithmic framework was the top-performing entry in the MICCAI 2013 Multimodal Brain Tumor Segmentation challenge and, to our knowledge, is the only entry for both challenge years (2012 \& 2013) which has been made publicly available.
\end{abstract}

>>>>

\begin{abstract} 
Automated brain tumor segmentation in MRI is complicated by the lack
of prior knowledge concerning tumor location, spatial extent, shape,
possible displacement of normal tissue, and intensity signature.
These factors limit the applicability of techniques with established
performance in related tasks such as normal brain tissue segmentation.
We introduce a template-based framework for computing geometric and
asymmetry-driven feature sets from multiple modality neuroimaging.  We
use these features to drive a supervised whole-brain and tumor segmentation
approach based on random forests.  The asymmetry-related features 
demonstrate excellent discriminative properties within this framework. 
This approach is made possible by symmetric multimodality brain templates which are optimal
in terms of both shape and multivariate intensity.  Further
performance improvements are demonstrated by a successive application
of random forest models for increasing levels of feature refinement to
which we refer as {\it concatenated random forests}.  Although the
derived workflow involves many disparate components, the newly
developed \textit{ANTsR} open source software package significantly facilitates
the proposed methodology.  \textit{ANTsR} is a comprehensive interface between the
popular Advanced Normalization Tools (ANTs) and the \textit{R}
statistical project. \textit{ANTsR} integrates proven image analysis methods
for image registration, segmentation, bias correction, and
template building with \textit{R}'s statistical and machine
learning techniques and state-of-the-art visualization possibilities.  
The reported algorithmic framework was the
top-performing entry in the MICCAI 2013 Multimodal Brain Tumor
Segmentation challenge and, to our knowledge, is the only entry for
both challenge years (2012 \& 2013) which has been made publicly
available.
\end{abstract}
